Comparing MTurk and the US Population's Occupational Diversity

### 2018-12-22 Manuscript.Rmd

---
title             : "Comparing the Occupational and Demographic Diversity of Amazon's Mechanical Turk to the U.S. Labor Force"
shorttitle        : "MTurk's Occupational Diversity"

author: 
  - name          : "Christopher M. Castille"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "906 E. 1st St., Thibodaux, LA, 70301"
    email         : "chris_castille@mac.com"
  - name          : "Kathryn Daigle"
    affiliation   : "1"
  - name          : "Sarah Avet"
    affiliation   : "1"
  - name          : "Rachel L. Williamson"
    affiliation   : "2"
  - name          : "John E. Buckner"
    affiliation   : "3"
  - name          : "Bodour H. Mahmoud"
    affiliation   : "4"
  - name          : "James DeLeon"
    affiliation   : "5"
affiliation:
  - id            : "1"
    institution   : "Nicholls State University"
  - id            : "2"
    institution   : "Louisiana State University"
  - id            : "3"
    institution   : "AlixPartners"
  - id            : "4"
    institution   : "Villanova University"
  - id            : "5"
    institution   : "APTMetrics"

author_note: >
  All correspondence should be sent to the lead author at chris_castille@mac.com. We would like to thank Bryan Bunn and Maximillian Sinn for taking the time to offer a friendly review of this manuscript.

abstract: >
  We compare the occupational diversity of three conveniently gathered MTurk samples (two in 2015, one in 2017) against the broader US labor force from which they have been indirectly sampled. We focus on occupational diversity given concerns regarding the the generalizability of findings into organizational life that have been drawn from studies utilizing MTurk. Additionally, as researchers may hope to target specific populations (e.g., sales professionals) understanding the extent to which these professionals are over- or under- represented in the MTurk population would inform decisions regarding the cost-effectiveness of sampling techniques. Across our samples, we found differences suggesting that the MTurk population is generally overrepresented by white collar professionals (though this is an imperfect trend). Other demographic trends were also explored regarding age, gender, and education. Overall, the MTurk population appears to fall short of an ideal representation of the broader labor force.

@@

wordcount         : "3000"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---
```{r Load Packages, include=FALSE}
# Load packages
library(papaja)         # Print in apa style
library(readr)          # Reading data
library(readxl)         # Reading data
library(data.table)     # Reading data
library(openxlsx)       # Reading data
library(binom)          # Confidence intervals for proportions
library(apa)            # Print results in apa format
library(pwr)            # Power analysis tools
library(RVAideMemoire)  # Conduct post-hoc test
library(ggplot2)        # Graphing results
library(scales)         # For printing frequencies as percentages
library(tidyquant)      # Used in demographic analysis
library(lsr)            # Useful for conducting one-sample t-tests and estiamting Cohen's D
library(stringr)        # Package helps us analyze Rachel's data
library(tidyr)          # Package helps us analyze Rachel's data 
library(packrat)        # Enhance reproducibility
```
# Introduction
Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population [@aguinisConductingFieldExperiments2012; @behrendViabilityCrowdsourcingSurvey2011; @bergmanWhereHaveAll2016; @paolacciTurkUnderstandingMechanical2014; @shankUsingCrowdsourcingWebsites2016]. Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena [e.g., reaction times, priming, task switching, see @crumpEvaluatingAmazonMechanical2013; memory, see @simonsCommonMisBeliefs2012 and by organizational behavior (OB) researchers to expand the OB literature [e.g., @yarkoniInteractionsDonorAgreeableness2015].

Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation [@landersInconvenientTruthArbitrary2015; @wooAmazonMechanicalTurk2015] and other yet-to-be-identified constraints. Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk. Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting, understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings. By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies [@griggsWhoAreThese2016].

# Review of the Literature

## What is MTurk?
MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee [@landersInconvenientTruthArbitrary2015]. Billed as a “marketplace for work that requires human intelligence”, MTurk allows “requesters” to post Human Intelligence Tasks (HITs), which serve as self-contained jobs in which “workers” can participate. Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete. Workers are given a short description about a project, including details about various tasks, estimated time investment, and payment, and may selectively choose which projects to complete. Here, researchers seeking participants often post survey studies for workers to voluntarily complete.

## The Value of Studying Working Populations with MTurk

MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations . The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@masonConductingBehavioralResearch2012]. Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure [@paolacciRunningExperimentsAmazon2010]. More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon [@buhrmesterAmazonMechanicalTurk2011; @erikssonWhatAmericansKnow2012; @paolacciRunningExperimentsAmazon2010]. For instance, @behrendViabilityCrowdsourcingSurvey2011 found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality. The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings [@paolacciRunningExperimentsAmazon2010], which has been a key concern facing OB research [@henrichWeirdestPeopleWorld2010].

However, while researchers have praised MTurk for its diversity, few organizational behavior researchers have considered how MTurk might be less diverse than expected in a key respect: occupational diversity. To our knowledge, no study has compared the occupational diversity of MTurk to the broader US population. While @behrendViabilityCrowdsourcingSurvey2011 work suggests that MTurk’s occupational diversity is greater than the university population, our work expands on their research by comparing MTurk’s occupational diversity to the broader US population. If the occupational diversity of the broader US population is indeed reflected in MTurk, findings from MTurk should better generalize across occupations. Alternatively, if MTurk’s occupational diversity over- or under-represent certain occupations, generalizability of findings from MTurk should be more limited.

*Research Question 1: Is the occupational diversity of the MTurk population representative of the broader US labor force?*

In addition to examining occupational diversity, we conducted exploratory analyses of other demographic disparities, focusing in on age, gender, ethnicity, and education as these are commonly studied in the social sciences. Therefore, a second research question was examined, but in an exploratory fashion. Answering this question required that we describe the diversity of the US labor force. Fortunately, the BLS provides summary statistics which describe the proportion of individuals falling into various demographic categories.

*Research Question 2: Is the demographic diversity of the MTurk population representative of the broader US labor force?*

@@

## US Population Occupational Summary Statistics

Occupational Employment Statistics were obtained from the United States Bureau of Labor Statistics (BLS) both from years 2015 and 2017. These data are released annually in the spring and describe the previous year. Statistics from these reports allowed us to define expectations regarding the proportion of workers falling into a particular intermediate occupational category. We adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the Bureau of Labor Statistics (BLS) for this study to ease our analysis.

@@

# Build the BLS Table, but first establish a temp file. Unhastag to use.
# Download the file with download.file()
# Here is the URL: 
# download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
# unzip("BLS2015.zip")
BLS <- read_excel("oesm15nat/national_M2015_dl.xlsx")
BLS <- BLS[c(2,4)]

@@

# Delete unneeded data.
LATech <- LATech[c(1:3)]

@@

# Remove unemployed cases.
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

LATech <- completeFun(LATech, "O*NET Job Code")

@@

# UGA data
UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
UGA <- UGA[c(2,21)]
# Edit data. Some individuals could be classified under O*NET, but weren't in this previous investigation. Keep in mind that only the first two numbers really matter, so if there are errors (and they be random) then they should wash out at the high level of the hierarchy.

@@

# Run chi-square test for sample 1
x15.1 <- chisq.test(table$n1, p = round(table$`Expected`,3))
# Results are significant. Agresti (2007) notes that standardized residuals greater than 2 are indicative of association. Positive residuals indicate over-representation, while a negative residual indicates a negative association. The error bars in the figure also capture this information. 
x15.1[["stdres"]]
# Significantly over-represented: (i) 11-13 Management, Business, and Financial (6.94), (ii) 15-19 Computer, Engineering, and Science (11.97), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (8.17).
# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (0.58), (ii) 41 Sales and Related (-2.47), (iii) 43 Office and Administrative Support (1.15), (iv) 45 Farming, Fishing, and Forestry (-0.22), and (v) 55 Military Specific (-1.37).
# Significantly under-represented: (i) 31-39 Service (-6.33), (ii) 47 Construction and Extraction (-3.40), (iii) 49 Installation, Maintenance, and Repair (-4.51), (iv) 51 Production (-5.47), and (v) 53 Transportion and Material Moving (-5.69).

# Run chi-square test for sample 2
x15.2 <- chisq.test(table$n2, p = round(table$`Expected`,3))
# Results are significant. Run post-hoc pairwise comparisons. 
x15.2[["stdres"]]
# Significantly over-represented: (i) 11-13 Management, Business, and Financial (14.76), (ii) 15-19 Computer, Engineering, and Science (8.52), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (7.30).
# Conforming with expectations: (i) 41 Sales and Related (-1.70), (ii) 43 Office and Administrative Support (1.17), (iii) 45 Farming, Fishing, and Forestry (0.43), and (iv) 55 Military Specific (-1.76).
# Significantly under-represented: (i) 29 Healthcare Practitioners and Technical (-3.32), (ii) 31-39 Service (-5.57), (iii) 47 Construction and Extraction (-4.72), (iv) 49 Installation, Maintenance, and Repair (-5.98), (v) 51 Production (-5.44), and (vi) 53 Transportion and Material Moving (-7.29).

@@

# C217 data
C217 <- read_excel("2017 Data.xls")

# Delete unneeded data.
C217 <- C217[c(12, 20:21)]
names(C217) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")

# Edit data. Some participants provided incorrect codes or no codes.
C217[153, 3] = "43-3011.00" 
C217[412, 3] = "43-5081.03" # Provided two codes; picked the first code.
C217[612, 3] = "43-3031.00"
C217[644, 3] = "41-9031.00"
C217[274,] = c("analyst", "analyst", "13-0000.00")

# Remove unemployed cases.
C217 <- completeFun(C217, "O*NET Job Code")

@@

# Run chi-square test for sample 3
x17.1 <- chisq.test(table3$n3, p = round(table3$`Expected`,3))
# Results are significant. Agresti (2007) notes that standardized residuals greater than 2 are indicative of association. Positive residuals indicate over-representation, while a negative residual indicates a negative association. The error bars in the figure also capture this information. 
x17.1[["stdres"]]
# Significantly over-represented: (i) 11-13 Management, Business, and Financial (8.23), (ii) 15-19 Computer, Engineering, and Science (9.56), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (6.30).
# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (-2.52), (ii) 41 Sales and Related (-2.23), (iii) 43 Office and Administrative Support (2.36), (iv) 45 Farming, Fishing, and Forestry (1.42), (v) 49 Installation and Maintenance (-2.10), and (vi) 55 Military Specific (-1.02).
# Significantly under-represented: (i) 31-39 Service (-6.05), (ii) 47 Construction and Extraction (-4.68), (iii) 51 Production (-4.47), and (iv) 53 Transportion and Material Moving (-5.57).
```

>>>>

---
title             : "Comparing the Occupational and Demographic Diversity of the Labor Force that is Accessible via MTurk (United States)"
shorttitle        : "MTurk's Occupational Diversity"

author: 
  - name          : "Christopher M. Castille"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "906 E. 1st St., Thibodaux, LA, 70301"
    email         : "chris_castille@mac.com"
  - name          : "Kathryn Daigle"
    affiliation   : "1"
  - name          : "Sarah Avet"
    affiliation   : "1"
  - name          : "Rachel Williamson Smith"
    affiliation   : "2"
  - name          : "James DeLeon"
    affiliation   : "3"
  - name          : "Bodour H. Mahmoud"
    affiliation   : "4"
  - name          : "John E. Buckner"
    affiliation   : "5"

affiliation:
  - id            : "1"
    institution   : "Nicholls State University"
  - id            : "2"
    institution   : "Louisiana State University"
  - id            : "3"
    institution   : "APTMetrics"
  - id            : "4"
    institution   : "Villanova University"
  - id            : "5"
    institution   : "AlixPartners"

author_note: >
  We have sought to make this project fully reproducible. All project materials can be found on the Open Science Framework (https://osf.io/r7mjt/), where elements of this study were pre-registered (https://osf.io/fdgew/). A previous version of this manuscript was presented at the 2017 annual conference for the Society for Industrial & Organizational Psychology, Inc., in Orlando, FL. It should also be noted that data collection for one of the 2015 samples was funded by the Graduate School Dean's Award Program at the University of Georgia.

abstract: >
  Scholars interested in studying behavioral phenomena of relevance for organizational settings have increasingly relied upon Amazon's Mechanical Turk. MTurk offers opportunities for examining a wide range of occupational settings, greatly expanding the ability of scholars' ability to generate generalizable inferences from sample data. However, little research has compared the occupational makeup of the labor force that is accessible via MTurk to the broader labor force from which they are indirectly sampled. This is crucial to understand given the importance of the work context for organizational scholarship. Here, we compare the occupational diversity of three conveniently gathered MTurk samples (two in 2015, one in 2017) against the broader broader labor force from which they have been indirectly sampled in the United States. Across our samples, we consistently found differences suggesting that the MTurk population is generally overrepresented by certain white-collar professions (e.g., Management, Business, and Financial; Computer, Engineering, and Science; Education, Legal, Community Service, Arts, and Media) and underrepresented by blue-collar professions (e.g., Production; Transportation and Material Moving). Other demographic trends mirrored broader demographic trends identified with prior MTurk research with regard to age (younger), gender (female-biased), ethnicity (e.g., African Americans underrepresented), and education (generally overeducated). Overall, our conclusions mirror add to the published literature by indicating that the labor force that is accessible via MTurk does not reflect the broader labor force.

@@

wordcount         : "3919"

@@

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_docx
---
```{r Load Packages, include=FALSE}
# Load packages
library(papaja)         # Print in apa style
library(dplyr)          # Manipulating data
library(citr)           # Citation assistance
library(readr)          # Reading data
library(readxl)         # Reading data
library(openxlsx)       # Reading data
library(binom)          # Confidence intervals for proportions
library(apa)            # Print results in apa format
library(pwr)            # Power analysis tools
library(RVAideMemoire)  # Conduct post-hoc test
library(ggplot2)        # Graphing results
library(scales)         # For printing frequencies as percentages
library(tidyquant)      # Used in demographic analysis
library(lsr)            # Useful for conducting one-sample t-tests and estimating Cohen's D
library(stringr)        # Package helps us analyze the UGA data
library(tidyr)          # Package helps us analyze the UGA data 
library(rIP)            # Facilitates screening data for bots
library(DataCombine)    # Adding rows to tables to allow easier reading
```
# Introduction

Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has been popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population for well [@aguinisConductingFieldExperiments2012; @ahlerMicroTaskMarketLemons2018; @bergmanWhereHaveAll2016; @behrendViabilityCrowdsourcingSurvey2011; @kennedyShapeSolutionsMTurk2018; @landersInconvenientTruthArbitrary2015; @paolacciTurkUnderstandingMechanical2014]. The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@masonConductingBehavioralResearch2012], subject anonymity or identifiability (which is important for longitudinal studies), and offers a simple and supportive infrastructure [@paolacciRunningExperimentsAmazon2010]. Leveraging the strengths of this tool, MTurk has been used to replicate a variety of well-known phenomena in the social sciences [e.g., reaction times, priming, task switching, see @crumpEvaluatingAmazonMechanical2013; memory, see @simonsCommonMisBeliefs2012].

Scholars who study organizational phenomena (e.g., organizational behaviorists, industrial and organizational psychologists, management scholars) have also adopted MTurk. @keithSystemsPerspectiveAmazon2017 recently reported that published organizational science studies utilizing MTurk increased by 800% between 2012 and 2015. When comparing crowdsourcing tools like MTurk with traditional methods of studying organizational phenomena [e.g., gaining consent from both institutional review boards and local organizations; see @ilgenConductingIndustrialOrganizational2001], several benefits are particularly salient, such as rapidly gaining access to multiple organizational settings and enhanced external validity. Such benefits can greatly reduce the cost of studying organizational phenomena, leveling the research playing field [@goodmanDataCollectionFlat2013].

As enthusiasm surrounding the use of MTurk in the organizational sciences has grown, so have scholars' concerns over its use [e.g., @cheungAmazonMechanicalTurk2017; @landersInconvenientTruthArbitrary2015; @keithSystemsPerspectiveAmazon2017; @wooAmazonMechanicalTurk2015]. One problematic area relates to an assumption underlying research into organizational phenomena that draws on MTurk; namely, that the MTurk workers themselves represent a broad cross-section of the labor force population. This assumption is key to a commonly cited benefit of using crowdsourcing tools like MTurk; that is, increased generalizability [e.g., @aguinisConductingFieldExperiments2012; @behrendViabilityCrowdsourcingSurvey2011; @highhouseNewFruitFly2015; @keithSystemsPerspectiveAmazon2017; @roulinDonThrowBaby2015]. In other words, organizational scholars may assume that MTurk can be used to indirectly and *adequately* sample from the broader working population. Unfortunately, little research has compared MTurk worker demographics to that of the broader labor force. If MTurk does not adequately reflect the broader labor force, then the generalizability of research drawing on MTurk will have its own set of constraints [@keithSystemsPerspectiveAmazon2017; @landersInconvenientTruthArbitrary2015].

Here, we compare the working subpopulation of the U.S. MTurk workforce to the broader labor force from which they were indirectly sampled. Given the importance of context in organizational research [@johnsEssentialImpactContext2006; @judgeBrightDarkSides2007; @newmanExternalValidityMultiorganization2015], we focus specifically on the extent to which the labor force that is sampled via MTurk adequately represents the broader labor force. Our study, which fits into the broader body of literature regarding who we study and the generalizability of claims made in the social sciences [e.g., @paolacciRunningExperimentsAmazon2010; @henrichWeirdestPeopleWorld2010], thus contributes to the wealth of knowledge that exists on the demographics of the MTurk population. It also informs future research on the study of organizational phenomena via MTurk.

# Examining the Occupational and Demographic Makeup of the U.S. Labor Force that is Sampled Indirectly from Amazon's Mechanical Turk

Over half of the MTurk population is employed [@behrendViabilityCrowdsourcingSurvey2011; @keithSystemsPerspectiveAmazon2017; @levayDemographicPoliticalComposition2016]. If the total MTurk population contains over 100,000 people [@difallahDemographicsDynamicsMechanical2018], there is a sizable subpopulation of individuals whom we may invite to participate in our research. Even if only a few thousand individuals can be sampled from [see @stewartAverageLaboratorySamples2015], this can still be helpful for organizational scholarship (e.g., measurement refinement). It might even be useful for examining understudied phenomena or populations of workers [e.g., job search behavior, underemployment, unemployed; see @roulinDonThrowBaby2015].

By using MTurk to sample workers from a wide range of occupational settings, it has widely been believed that scholars' ability to generate inferences with greater external validity from sample data has increased [@aguinisConductingFieldExperiments2012; @highhouseNewFruitFly2015; @smithConvenientSolutionUsing2015]. MTurk's diversity on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality [@behrendViabilityCrowdsourcingSurvey2011] is commonly cited as a strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for organizational scholars to draw upon [@buhrmesterAmazonMechanicalTurk2011; @erikssonWhatAmericansKnow2012; @paolacciRunningExperimentsAmazon2010].

While several studies have examined the attributes of the MTurk population [e.g., demographic, occupational, psychographic, etc.; see @behrendViabilityCrowdsourcingSurvey2011; @michelAmazonMechanicalTurk2018], only one has compared the occupational makeup of MTurk [i.e., @michelAmazonMechanicalTurk2018]. By comparing the occupational makeup (or occupational heterogeneity or diversity) of a sample of U.S. MTurk respondents to the labor force, @michelAmazonMechanicalTurk2018 inferred that MTurk workers are broadly sampled from various occupational areas. For instance, they noted that the largest MTurk subpopulation was from the "Education and Training" career cluster, comprising approximately 13% of responses. They point out that a majority of the career clusters were within a 5% difference range when compared with corresponding career clusters as defined by the Bureau of Labor Statistics. They also point out that the most undersampled population was "Business Management and Administration."

Michel et al.'s (2018) study is important for prompting conversation about how the occupational diversity of MTurk compares to the broader labor force. However, while informative, Michel et al.'s (2018) study has notable shortcomings that we sought to overcome. First, Michel et al. sought to determine if MTurk workers are broadly distributed across the labor market. While they did indeed answer this question, a statistical test would challenge a key assumption that might be adopted (implicitly or explicitly) by organizational researchers who use MTurk; namely, that the labor force accessed through MTurk is comparable to the broader labor force. Examining this assumption statistically is important because if we cannot assume that MTurk gives us a comparable cross section of the labor force, then our conclusions will be biased in favor of over- or under-sampled sampled areas. It is also worth pointing that that, since we have data spread across multiple years (2015 and 2017), we have an opportunity to examine the pervasiveness of trends in occupational and demographic makeup of the workforce that is accessed via MTurk. If MTurk has a particular and pervasive bias in favor of certain occupational areas, then increasing our reliance on MTurk might will not bring about the purported benefits. Rather, such a growing reliance will prevent us from overcoming concerns that our knowledge base applies only to certain kinds of workers [e.g., core, salaried, managerial; @bergmanWhereHaveAll2016].

Second, Michel et al. relied on labor force descriptions from 2013. If we assume that Michel et al.'s data were also gathered in the same year, then - given that roughly half of the workers leave MTurk within each year [@difallahDemographicsDynamicsMechanical2018; @stewartAverageLaboratorySamples2015] - Michel et al.'s conclusions may no longer accurately describe the labor force that is accessible via MTurk. Having some idea regarding the composition of the labor force that is accessible via MTurk can inform sampling practices. For instance, if a researcher hopes to examine sales professionals, then knowing whether or not this population is historically underrepresented by MTurk can be useful for deciding whether or not to sample workers from MTurk.

In sum, though prior work suggests that the labor force that is accessible via MTurk is quite diverse in terms of occupations, our work expands the literature by (1) clarifying the extent to which this heterogeneity aligns with the broader and indirectly sampled labor force and (2) showing the pervasiveness of these trends. If the occupational diversity of the broader U.S. population is indeed reflected by MTurk, then findings from MTurk's labor force should better generalize across occupations. Alternatively, if MTurk’s occupational diversity consistently over- or under-represents certain occupations, then the generalizability of findings from MTurk may be more limited than has been appreciated. Therefore, we begin our investigation by clarifying our focal research question.

*Research Question 1: Does the occupational diversity of the labor force that is accessible via MTurk adequately represent the broader U.S. labor force?*

In addition to examining the occupational makeup of the labor force that is accessible via MTurk, we examine other demographic attributes, focusing in on age, gender, ethnicity, and education, as these are commonly studied in the organizational sciences [e.g., @berryInterpersonalDevianceOrganizational2007; @collinsRaceJobApplicants1998; @dalalMetaAnalysisRelationshipOrganizational2005]. While there is much prior research on MTurk, it describes broad trends associated with the MTurk population in general, which may or may not generalize to the subpopulation that is also part of the labor force. For the U.S., the general MTurk population seems to be younger and slightly female-biased [@difallahDemographicsDynamicsMechanical2018]. Compared to college students and community samples, it is more diverse in terms of education [@behrendViabilityCrowdsourcingSurvey2011; @goodmanDataCollectionFlat2013]. In comparing MTurk samples to nationally representative samples (e.g., U.S. Census, Survey USA), @keithSystemsPerspectiveAmazon2017 also note that MTurk samples are younger, more educated. Knowing the extent to which the labor force that is accessible via MTurk mirrors the broader labor force, demographically speaking, would also be informative for the same reasons noted for RQ1. Given that no prior work has conducted this comparison, we sought to answer a second research question.

*Research Question 2: Does the demographic diversity (age, gender, ethnicity, and education) of the labor force that is accessible via MTurk adequately represent of the broader U.S. labor force?*

@@

## U.S. Population Occupational Information

Occupational Employment Statistics were obtained from the BLS (BLS) both from years 2015 and 2017 to correspond with the MTurk samples, which were also gathered from the same years. These years for chosen because those are the years for which we have relevant data on MTurk. The BLS data are released annually in the spring and describe the previous year. Statistics from these reports allowed us to define expectations regarding the proportion of workers falling into a particular occupational category. For the sake of consistency, we adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the BLS for this study.

@@

# Build the BLS Table, but first establish a temp file. Unhastag to use.
# Download the file with download.file()
# Here is the URL: 
# download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
# unzip("BLS2015.zip")
BLS <- read_excel("Data/oesm15nat/national_M2015_dl.xlsx")
BLS <- BLS[c(2,4)]

@@

# Delete unneeded variables.
LATech <- LATech[c(1:3)]

@@

# Filter out cases from foreign countries and questionable IP addresses.
# Conditionally delete cases that were flagged for being either out of the country (C) or blocked B (B).
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Co-FOunder"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="senior analyst"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Supply Chain Cordinator"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assistant Manager" & LATech$`O*NET Occupation Title` =="First-Line Supervisors of Food Preparation and Serving Workers"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="residential care aide"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Receptionist"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Global Training Lead"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="residential care worker"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Navigation Officer"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assembly Supervisor"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="x-ray tech"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Financial Analyst"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Financial Advisor" & LATech$`O*NET Occupation Title` =="Financial Managers, Branch or Department"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Project Manager" & LATech$`O*NET Occupation Title` =="Information Technology Project Managers"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Manufacturing Engineer"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Computer Programmer"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Staff Assistant"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Communications Engineer"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="engineering apprentice"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="IT specialist"),] # C
LATech <-LATech[-c(511),] # C Deleting a random cashier because we cannot identify which cashier was from Nepal. 
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Telephone systems analyst"),] # C
LATech <-LATech[-c(697),] # C Deleting a random plumber because we cannot identify which plumber was from the Philippines. 
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="photo editor"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Hydro-Tech III"),] # C
LATech <-LATech[-c(147),] # C Deleting a random software engineer because we cannot identify which software engineer was from Sweeden.
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Carpenter" & LATech$`O*NET Occupation Title` =="Carpenter"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Retail Sales Associate"),] # C
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Manufacturing Producer"),] # B
LATech <-LATech[-c(488),] # B Deleting a random nanny because we cannot identify which nanny was questionable
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Process Engineer"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Account Manager"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="engineer" & LATech$`O*NET Occupation Title` =="media engineer"),] # B
LATech <-LATech[-c(538),] # B Deleting a random sales associate because we cannot identify which sales associate was questionable.
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Social Worker"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="producer"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Stock Clerk"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="therapist"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Stockboy"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Production engineer Lead"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="TSO"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Multimedia Animator"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assistant Seafood Manager"),] # B
LATech <-LATech[-c(147),] # B Deleting a random software engineer because we cannot identify which software engineer was questionable.
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Accounts Payable clerk"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Customer Service Staff"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="PSD"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Special Education"),] # B
LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Pharmacisy technician"),] # B

# Remove unemployed cases.
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
LATech <- completeFun(LATech, "O*NET Job Code")

@@

# UGA data
UGA <- read_csv("Data/Rachel's Data from 2015.csv")

# Filter out cases from foreign countries and questionable IP addresses.
UGA <- filter(UGA, countryName == "United States") # Results in a loss of 46 cases. According to the Mechanical Turk Worker Website FAQ, US citizens are not allowed to work on MTurk. We therefore deemed cases falling outside the US as questionable and ommitted them from our studies. 
UGA <- filter(UGA, block == "0") # Results in a loss of 22 cases (though 25 cases were flagged for questionable IP addresses).
# retain only needed variables
UGA <- UGA[c(2,21)] 
# Edit data. Some individuals could be classified under O*NET, but weren't in this previous investigation. Keep in mind that only the first two numbers really matter, so if there are errors (and they be random) then they should wash out at the high level of the hierarchy.

@@

# Run chi-square test for sample 1
x15.1 <- chisq.test(table$n1, p = round(table$`Expected`,3))
# Results are significant. Agresti (2007) notes that standardized residuals greater than 2 are indicative of association. Positive residuals indicate over-representation, while a negative residual indicates a negative association. The error bars in the figure also capture this information. 
x15.1[["stdres"]]

# Run chi-square test for sample 2
x15.2 <- chisq.test(table$n2, p = round(table$`Expected`,3))
# Results are significant. Run post-hoc pairwise comparisons. 
x15.2[["stdres"]]

@@

# 2017 data
C217 <- read_csv("Data/C217.csv")
C217 <- C217[c(12, 20:21, 258, 259)]
names(C217) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code", "countryName", "block")
C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-3011.00	Bill and Account Collectors"] = "43-3011.00" 
C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-5081.03 and 41-4012.00"] = "43-5081.03" # Provided two codes; picked the first code.
C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-3031.00 - Bookkeeping, Accounting, and Auditing Clerks"] = "43-3031.00"
C217$`O*NET Job Code`[C217$`O*NET Job Code` == "42-9031.00"] = "41-9031.00"

# Filter out cases from foreign countries and questionable IP addresses.
C217 <- filter(C217, countryName == "United States") # Results in a loss of 30 cases. According to the Mechanical Turk Worker Website FAQ, US citizens are not allowed to work on MTurk. We therefore deemed cases falling outside the US as questionable and ommitted them from our studies. 
C217 <- filter(C217, block == "0") # Results in a loss of 21 cases (though 25 cases were flagged for questionable IP addresses).
# drop the two auxiliary variables
C217 <- C217[c(-4,-5)]

# Address missing data for one case.
C217[274,] = c("analyst", "analyst", "13-0000.00")

@@

# Run chi-square test for sample 3
x17.1 <- chisq.test(table3$n3, p = round(table3$`Expected`,3))
# Results are significant. Agresti (2007) notes that standardized residuals greater than 2 are indicative of association. Positive residuals indicate over-representation, while a negative residual indicates a negative association. The error bars in the figure also capture this information. 
x17.1[["stdres"]]
```
```{r 2015 Demographic Analysis, warning = FALSE, echo = FALSE, include = FALSE}
# Age
BLS_age_15 <- read_excel("Data/BLS.Age.2015.xlsx")
